---
title: "Testing Function"
author: "Lara Charlotte Kuberka"
date: "2023-10-31"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Packages, include=FALSE}
library(dplyr)
```

#### Function 

- Creating a function to transform data into a tibble and appending user defined vector to data set
- x = dataset, y = user-defined vector

```{r}
data_as_tibble <- function(x, y) {
  x = cbind(x,y)
  x = as_tibble(x)
  return(x)
}
```

#### Loading Dataset from R:
```{r}
data(sleep)
```

#### user- defined data as vector:
```{r}
timezone <- c("CET", "GMT", "EST","CET", "GMT", "EST","CET", "GMT", "EST", "CET","CET", "GMT", "EST","CET", "GMT", "EST","CET", "GMT", "EST", "CET")
```


#### using data with function to show the functionalities of function
```{r}
data_as_tibble(sleep,timezone)
```

This function has created a tibble from the given dataset and appended user-defined data in form of a vector to extend the data frame according to the user's wishes.



